\documentclass{article}

\usepackage{geometry}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{pgfplots}


\newcommand{\mail}[1]{
  \href{mailto:#1}{#1}
}

\geometry{
  top=2cm,
  bottom=2cm,
  right=3cm,
  left=3cm
}

\pgfplotsset{
  compat=1.13,
  every axis/.prefix style={
    width=.8\textwidth,
    height=200pt,
    legend cell align=left
  },
  every axis plot/.style={
    no marks,
    line width=.8pt
  }
}

\begin{document}

\begin{center}
  \textbf{
    \LARGE Deep Learning with Stacked AEs \& RBMs \\
    \vspace{.5ex}
    \large DD2437 - Artificial Neural Networks \& Deep Architectures - Lab 4\\
    \vspace{1ex}
    \large
    \begin{tabular}{ccc}
      Niels Agerskov & Lukas Bjarre & Gabriel Carrizo \\
      \mail{agerskov@kth.se} & \mail{lbjarre@kth.se} & \mail{gabcar@kth.se}
    \end{tabular}
  } \\
  \vspace{.5ex}
  \rule{\textwidth}{0.4pt}
\end{center}

This lab will examine two different artificial neural network structures,
Auto Encodes (AE) and Restricted Boltzmann Machines (RBM).
Their effectiveness in a learning task 
and the effect of the layer depth of the models
will be tested and evaluated.

\section{Feature learning}
In this first task shallow versions of both models are trained
as benchmarks for the later deeper versions.
The dataset used is a subset of the MNIST dataset
containing $28 \times 28$ images of handwritten digits from 0 to 9
together with correct labels of the written digit.
All the pixel values has for simplicity's sake been converted to binary values
via simple thresholding.

The input size hyperparameter for both of the models is decided by the shape of the data.
In our case we require $28 \times 28 = 784$ input nodes, one for each image pixel.
We do however have a choice in the number of hidden units.

\begin{figure}[!ht]
  \centering
  \begin{tikzpicture}
    \begin{axis}[
      title=\textbf{RBM training results},
      xlabel={Epoch},
      ylabel={Validation error},
    ]
      \foreach \color/\hiddenunits in {10/50, 40/75, 70/100, 100/150} { 
        \edef\temp{
          \noexpand\addplot +[
            color=red!\color!blue
          ]
          table [
            x index=0,
            y index=2,
            col sep=comma
          ]
          {../data/rbm_hidden_20e_\noexpand\hiddenunits.csv};
          \noexpand\addlegendentry{$n_{\text{hidden}} = \hiddenunits$}
        }
        \temp
      }
    \end{axis}
  \end{tikzpicture}
  \caption{Error curves on the validation set for the RBM.}
  \label{fig:rbmtraining}
\end{figure}

\end{document}

